Paper 3 - Causal Roadmap

### 2023-04-12 docs/causal_roadmap.qmd
Started writing skeletons for functions for RQs.

Table with random seed, names, description, and version numbers of all software packages.

| **Name** | **Version** | **Description** |
|:---------|:------------|:----------------|
| Random seed | NA | Will be set to $X$ |
| `R` | `r I(paste0(R.version$major, ".", R.version$minor))` | Statistical programming environment |
| ... | ... | ... |

>>>>

Table with random seed, names, version numbers, and description of the main software packages.

| **Name** | **Version** | **Description** |
|:---------|:------------|:----------------|
| Random seed | NA | Will be set to $X$ |
| `R` | `r I(paste0(R.version$major, ".", R.version$minor))` | Statistical programming environment |
| `tlverse` | `r packageVersion("tlverse")` | Targeted Learning software ecosystem in R |
| `lmtp` | `r packageVersion("lmtp")` | Non-parametric Causal Effects of Feasible Interventions Based on Modified Treatment Policies |
| `sl3` | `r packageVersion("sl3")` | Super Learner ensemble machine learning |
| `labelled` | `r packageVersion("labelled")` | Manipulate metadata |
| `dlookr` | `r packageVersion("dlookr")` | Diagnose, explore, and transform data |
| `Hmisc` | `r packageVersion("Hmisc")` | Harrell Miscellaneous |
| `dagitty` | `r packageVersion("dagitty")` | Graphical Analysis of Structural Causal Models |
| `qreport` | `r packageVersion("qreport")` | Facilitating the composition of Quarto reports |
| ... | ... | ... |
